MINOS Handover Plots

### 2024-07-23 minos/validation/handovers.Rmd
Added spaghetti plots for pathway variables back to handovers

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, housing_quality)
# base.s <- base.dat %>%
#   select(pidp, age, time, housing_quality)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'housing_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, neighbourhood_safety)
# base.s <- base.dat %>%
#   select(pidp, age, time, neighbourhood_safety)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'neighbourhood_safety',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, loneliness)
# base.s <- base.dat %>%
#   select(pidp, age, time, loneliness)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'loneliness',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

@@

```{r}
# raw.nut <- raw.dat %>%
#   select(pidp, age, time, nutrition_quality)
# base.nut <- base.dat %>%
#   select(pidp, age, time, nutrition_quality)
# 
# nut.spag <- rbind(raw.nut, base.nut)
# 
# spaghetti_plot(nut.spag, 'nutrition_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# 
# density_ridges(nut.spag, "nutrition_quality", 
#                save = T, 
#                save.path = save.path)
# 
# rm(raw.nut, base.nut, nut.spag)
```

@@

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, education_state)
# base.s <- base.dat %>%
#   select(pidp, age, time, education_state)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'education_state',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

>>>>

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, housing_quality)
base.s <- base.dat %>%
  select(pidp, age, time, housing_quality)

spaghetti_plot(spag, 'housing_quality',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, neighbourhood_safety)
base.s <- base.dat %>%
  select(pidp, age, time, neighbourhood_safety)

spaghetti_plot(spag, 'neighbourhood_safety',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, loneliness)
base.s <- base.dat %>%
  select(pidp, age, time, loneliness)

spaghetti_plot(spag, 'loneliness',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}
raw.nut <- raw.dat %>%
  select(pidp, age, time, nutrition_quality)
base.nut <- base.dat %>%
  select(pidp, age, time, nutrition_quality)

nut.spag <- rbind(raw.nut, base.nut)

spaghetti_plot(nut.spag, 'nutrition_quality',
               save = shall.we.save,
               save.path = save.path)

density_ridges(nut.spag, "nutrition_quality",
               save = T,
               save.path = save.path)

rm(raw.nut, base.nut, nut.spag)
```

@@

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, education_state)
base.s <- base.dat %>%
  select(pidp, age, time, education_state)

spaghetti_plot(spag, 'education_state',
               save = shall.we.save,
               save.path = save.path)
